### 2021-12-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@7cce168731bec98eb0897cbd064f425372221f1e 🚀

>>>>

\hypertarget{illustration-on-empirical-food-webs}{%
\section{Illustration on empirical food
webs}\label{illustration-on-empirical-food-webs}}

In this section, we use a collection of XX empirical networks

\hypertarget{using-t-sbn-and-rdpg-to-simulate-arbitrarily-imperfect-classifier}{%
\subsection{Using t-SBN and RDPG to simulate arbitrarily imperfect
classifier}\label{using-t-sbn-and-rdpg-to-simulate-arbitrarily-imperfect-classifier}}

use t-SVD to only use some information

cumulative eigenvalues up to rank n give amount of information recovered

can be thresholded

how do values react to using fewer ranks

\hypertarget{effect-of-classifier-performance-on-metrics}{%
\subsection{Effect of classifier performance on
metrics}\label{effect-of-classifier-performance-on-metrics}}

\ldots{}
